Optimizing Abstract$^{\text 2}$ Machines

### 2012-11-11 paper/paper.tex

We discuss a variety of techniques for increasing performance by
decreasing the interpretive overhead of abstract interpretation. They
come in two flavors: decreasing the size of the represented state
space [SS], and decreasing intermediate data structures [DS].

\begin{itemize}
 \item{[SS] quotient by sets of values (lazy non-determinism)}
 \item{[SS] remove {\tt ev} states (abstract compilation)}
 \item{[DS] specialize the fixpoint operator to work with widened
   machine configurations (fixpoint specialization)}
 \item{[DS] operate on store changes rather than whole stores (store deltas)}
 \item{[DS] represent the store as a global, mutable hash and
   determine a state's store by the number of changes made to the
   global store at the time of visiting (timestamp)}
 \item{[DS] use a global mutable workset}
 \item{[DS] represent the global store as a global, mutable vector in
   the 0-CFA case. (preallocation)}
\end{itemize}
Each technique requires minimal changes to the reduction
relation/fixpoint, and each improves performance by integer
factors. The first four remain in the purely functional realm. The
final three use mutation in small, localized places, so they do not
increase conceptual complexity drastically.

@@

\subsection{Store deltas}

@@

% For David to fill in.
\subsection{Timestamp}
...
\subsection{Pre-allocated global store}
...

>>>>

We discuss a variety of techniques for increasing performance by
decreasing the interpretive overhead of abstract interpretation, all
in the purely functional realm. These techniques are the following:
\begin{itemize}
 \item{shrink state space by quotients (lazy non-determinism)}
 \item{shrink state space by removing {\tt ev} states (abstract
   compilation)}
 \item{decrease intermediate data structures by specializing our
fixpoint operator to work with widened machine configurations
(fixpoint specialization)}
 \item{decrease intermediate data structures by operating on store
   changes rather than whole stores (store deltas)}
\end{itemize}
Each technique requires minimal changes to the reduction
relation/fixpoint, and each improves performance by integer factors.

@@

\subsection{Computing with store changes}

@@

% For David to fill in.
\subsection{Imperative global store and worklist}
...
\subsection{Pre-allocated global store}
...
